\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-28 notes/2loopNLSM.tex
First paragraph on DC.

>>>>

\begin{figure}
  \begin{center}
    \begin{subfigure}{0.45\textwidth}
      \begin{center}
        \PhysicalCutOne{}{}{}{}
      \end{center}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
      \begin{center}
        \PhysicalCutTwo{}{}{}{}
      \end{center}
    \end{subfigure}
  \end{center}
  \caption{The two physical cut topologies shared by sGal, BI, and DBIVA}
  \label{fig:emu}
\end{figure}

With a cubic color-dual pion representation in hand, we can perfrom
double copies with many theories to extract ``gravitational''
amplitudes.  Such double-copy constructions are important nontrivial
checks on the underlying single-copy theories: the Jacobi relations in
the single copy conspire to produce the double-copy theory's version
of ``diff. invariance'' \citepls{}.  With pions as one of our single
copies, we will look at producing numerators for special Gallileons,
Born-Infeld theory, and DBIVA by double-copying against pions,
$\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively \citepls{}.
These output theories were recently studied extensively by one of the
authors and Carrasco from the perspective of direct unitarity cut
construction \cite{Carrasco:2023qgz}.  One of the shared features of
these 3 theories is that they all have the same physical cut
topologies in 4D: the two diagrams shown in \cref{fig:emu} which are
only composed of even-point amplitudes.
